\documentclass[10pt,draftclsnofoot,onecolumn,letterpaper]{article}
\usepackage{ragged2e}
\usepackage[svgnames,table]{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{listings}
\usepackage{graphicx}
    
\usepackage[utf8]{inputenc}
\usepackage[left=0.75in, right=0.75in, top=0.75in]{geometry}
    
\usepackage[T1]{fontenc}
\setlength{\parindent}{0pt}
    
    
\begin{document}
\begin{Center}
{\fontsize{14pt}{16.8pt}\selectfont OPEnS Pyranometer: IoT Solar Radiation Sensor\\ Executive Summary\par}
\end{Center}\par
    
\begin{Center}
Garen Porter, Brooke Weir, Alejandro Tovar\\
\end{Center}\par
\hrule
\vspace{5pt}


{\fontsize{12pt}{16.8pt}\selectfont \textbf{Documents Needing Verification}\par}
{\fontsize{10pt}{12.0pt}\selectfont There are four documents that need verification, first of which is the problem statement. This problem statement was the first group paper we submitted and it outlines why the pyranometer project is being sponsored and how we will gauge its completeness.\\\\The second document is the requirements document. The requirements document explains what our pyranometer should be able to do once it is finished. It goes over important criteria that the pyranometer must meet to be considered complete.\\\\The design document goes over how we plan to implement the various pieces of the pyranometer.\\\\The progress report is a high-level overview of what we have done throughout the fall term. It gives a week-by-week report of what we did; it shows where we feel we are at with regards to the project; it lists a set of goals we have using what we have done this term.\\
\par}\par

{\fontsize{12pt}{16.8pt}\selectfont \textbf{Winter Break Schedules: }\par}
{\fontsize{12pt}{16.8pt}\selectfont \textbf{Garen Porter: }\par}
{\fontsize{10pt}{12.0pt}\selectfont I will be working on campus 8:00am to 5:00pm, Monday through Friday over winter break. I am taking the week of Christmas off to visit my family. If the lab is open over the break I will try to work a few half days and spend some time working in the lab.\\
\par}\par

{\fontsize{12pt}{16.8pt}\selectfont \textbf{Brooke Weir: }\par}
{\fontsize{10pt}{12.0pt}\selectfont I will be in Beaverton, OR for most of winter break. For one week, I will be visiting family in California. I plan to work on CAD designs for the housing structure so the designs could be printed when we get back. Most of the work I plan to do will be remote. \\
\par}\par

{\fontsize{12pt}{16.8pt}\selectfont \textbf{Alejandro Tovar: }\par}
{\fontsize{10pt}{12.0pt}\selectfont I will not be in Oregon over winter break. I plan to start work on CAD designs on the dome structure. Also, I will do more research on diffusers and come up with a design for the diffuser as well.\\
\par}\par

{\fontsize{12pt}{16.8pt}\selectfont \textbf{Verification Process: }\par}
{\fontsize{10pt}{12.0pt}\selectfont Kirsten will send you a survey via email that asks whether you approve of our documents or not.\\
\par}\par
\end{document}